The error in Bayesian phylogenetic reconstruction when speciation is not instantaneous

### 2018-10-11 article.tex
Fix typo
Methods first paragraph

@@

\richel{Start new}
The PBD model has five parameters, depicted in table \ref{table:parameters}. 
The per species speciation completion rates $\lambda$ we use are $0.1$, $0.3$, $1.0$ and $10^9$. This means that there is a $0.15 dt$ ($0.35 dt$, $1.0 dt$, $10^9 dt$) probability of speciation completion occurring in an infinitesimal time $dt$. 
We use per species extinction rates of $\mu = \mu_g = \mu_i$ $0.0$, $0.1$ and $0.2$.
For each combination of $\lambda$, $\mu$ and $n$, we use a speciation initiation rate $b = b_i = b_g$ that gives a given value of the expected number of species. We use expected mean tree sizes $n$ of 50, 100 and 200 good taxa and the corresponding speciation initiation rates for all parameter combinations are shown in table \ref{table:pbd_parameters}.
Our parameters are inspired by existing work on protracted speciation \cite{etienne_and_rosindell_2012}\cite{etienne2014}.
We use $\lambda = 10^9 \approx \infty$ as our control for which the PBD model reduces to the BD model.

@@

See the supplementary information for a visualization of these sampling methods.
Based on the sampled species tree, we simulate a DNA alignment that has the same history
as this species tree, using the \verb;phangorn; package (\cite{phangorn}). 
We set the nucleotides of the DNA alignment to follow a Jukes-Cantor (\cite{jc69})
nucleotide substitution model, in which all nucleotide-to-nucleotide transitions
are equally likely. 
The DNA sequence of the root ancestor consists of four equally sized single-nucleotide blocks of adenine, cytosine, guanine and thymine respectively. 
For example, for a DNA sequence length of 12, this would be AAACCCGGGTTT. 
The order of nucletides does not matter in this study, 
because we do not consider several partitions of the sequence with their own parameters. 
Only the frequency of occurrence matters.
In our Bayesian inference (see below) we use the same site model as the (obviously correct) site model prior,
but we also explore the effect of assuming a more complex site model prior.
We predict with the more complex substitution model, 
that there will be more noise and hence our inference error will increase.
On the other hand, we dare not rule out that the inference error will decrease,
due to more flexibility in the more complex prior.
We set the mutation rate in such a way to maximize the information contained in the alignment.
To do so, we set the mutation rate such that we expect on average one (possibly silent) mutation per nucleotide
between crown age and present, which equates to $\frac{1}{15}$ mutations
per million years.
The DNA sequence length is chosen to provide a
resolution of $10^3$ years, 
% If sims take too long, we will decrease this resolution
that is, to have one expected nucleotide change 
per $10^3$ years per lineage on average. As one nucleotide is expected 
to have on average one (possibly silent) mutation per 15 million years, $15 \cdot 10^3$
nucleotides result in 1 mutation per alignment per $10^3$ years (which is
coincidentally the same as \cite{moller2018}). 
The simulation of these DNA aligments follows a strict clock model, 
which we will specify as one of the two clock models assumed in the Bayesian inference (see below).

>>>>

\newcommand*\mean[1]{\overline{#1}}

@@

The PBD model has five parameters, depicted in table \ref{table:parameters}. 
The per species speciation completion rates $\lambda$ we use are $0.1$, $0.3$, $1.0$ and $10^9$. 
This means that there is a $0.15\thinspace dt$ ($0.35\thinspace dt$, $1.0\thinspace dt$, $10^9\thinspace dt$) 
probability of speciation completion occurring in an infinitesimal time $dt$. 
We use per species extinction rates of $\mu = \mu_g = \mu_i$ $0.0$, $0.1$ and $0.2$.
We use tree sizes of $n$ of 50, 100 and 200 good taxa.
For each combination of $\lambda$, $\mu$ and $n$, 
we use a speciation initiation rate $b = b_i = b_g$ 
so that the expected mean number of species $\mathbf{E}(\mean{n}; b, \lambda, \mu)$,
given a $b$, $\lambda$ and $\mu$,
equals the desired number of species $n$.
$b$ is calculated using the PBD R package (\cite{pbd})
for each parameter combination and shown in table \ref{table:pbd_parameters}.
We use $\lambda = 10^9 \approx \infty$ as our control for which the PBD model reduces to the BD model.

@@

See the supplementary information for a visualization of these sampling methods.
Based on the sampled species tree, we simulate a DNA alignment that has the same history
as this species tree, using the \verb;phangorn; package (\cite{phangorn}). 
We set the nucleotides of the DNA alignment to follow a Jukes-Cantor (\cite{jc69})
nucleotide substitution model, in which all nucleotide-to-nucleotide transitions
are equally likely. 
The DNA sequence of the root ancestor consists of four equally sized single-nucleotide blocks of adenine, cytosine, guanine and thymine respectively. 
For example, for a DNA sequence length of 12, this would be AAACCCGGGTTT. 
The order of nucleotides does not matter in this study, 
because we do not consider several partitions of the sequence with their own parameters. 
Only the frequency of occurrence matters.
In our Bayesian inference (see below) we use the same site model as the (obviously correct) site model prior,
but we also explore the effect of assuming a more complex site model prior.
We predict with the more complex substitution model, 
that there will be more noise and hence our inference error will increase.
On the other hand, we dare not rule out that the inference error will decrease,
due to more flexibility in the more complex prior.
We set the mutation rate in such a way to maximize the information contained in the alignment.
To do so, we set the mutation rate such that we expect on average one (possibly silent) mutation per nucleotide
between crown age and present, which equates to $\frac{1}{15}$ mutations
per million years.
The DNA sequence length is chosen to provide a
resolution of $10^3$ years, 
% If sims take too long, we will decrease this resolution
that is, to have one expected nucleotide change 
per $10^3$ years per lineage on average. As one nucleotide is expected 
to have on average one (possibly silent) mutation per 15 million years, $15 \cdot 10^3$
nucleotides result in 1 mutation per alignment per $10^3$ years (which is
coincidentally the same as \cite{moller2018}). 
The simulation of these DNA aligments follows a strict clock model, 
which we will specify as one of the two clock models assumed in the Bayesian inference (see below).
